Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2022-12-28 paper-1/manuscript.tex
Rev sec Methods:Model (better refs to Fig1)

800 excitatory and 200 inhibitory neurons were placed randomly in a two-dimensional circular space with a radius of 4~mm, and formed synapses of weight $w = 1$ with 50 randomly selected postsynaptic partners within a range of 2~mm (excitatory) or 1~mm (inhibitory), reflecting the notion that excitatory neurons project over longer distances, while inhibitory neurons mainly connect to their local neighborhood. Connectivity and weights remained fixed throughout. Stimulation sites were evenly distributed 2.5~mm from the center of the dish, and stimulation delivered a one-time increase in $g_e$ to the 10 closest neurons, sufficient to trigger 2-3 spikes each. See Figure \ref{fig1}b and c for a representative example of the resulting network structure. Networks were pseudo-randomly generated according to the above scheme and screened for minimal stimulus response: Networks where fewer than 500 neurons responded to stimulation at any of the five sites after full recovery were discarded. In total, 30 networks were used for the experiments described below.

>>>>

800 excitatory and 200 inhibitory neurons were placed randomly in a two-dimensional circular space with a radius of 4~mm, and formed synapses of weight $w = 1$ with 50 randomly selected postsynaptic partners within a range of 2~mm (excitatory) or 1~mm (inhibitory), reflecting the notion that excitatory neurons project over longer distances, while inhibitory neurons mainly connect to their local neighborhood. Connectivity and weights remained fixed throughout. Stimulation sites were evenly distributed 2.5~mm from the center of the dish, and stimulation delivered a one-time increase in $g_e$ to the 10 closest neurons, sufficient to trigger 2-3 spikes each. Figure \ref{fig1}b shows a representative example of the resulting network structure, which we will be referring to as the sample network throughout this paper. In Figure \ref{fig1}c, we show the distance from the neurons stimulated at site 1 to each neuron in the network, in terms of the minimum number of excitatory synapses to reach the target, in order to give an intuition for how excitation may spread. In addition to the sample network, we generated additional networks for statistics purposes. Networks were pseudo-randomly generated according to the above scheme and screened for minimal stimulus response: Networks where fewer than 500 neurons responded to stimulation at any of the five sites after full recovery were discarded. In total, 30 networks were used for the experiments described below.
